\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles\\[1em] Supplementary material

### 2019-10-28 Response-NAR-Round1.tex

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[9pt,hyperref]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{amsmath} % for much better looking tables
\usepackage{xspace}
\usepackage{url}
\usepackage{soul}
\usepackage[table,x11names,dvipsnames]{xcolor}
\usepackage{amssymb} % for much better looking tables
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{ntheorem} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage{framed}
\usepackage{cabin}
\usepackage{tgtermes}
%\usepackage{tgadventor}
% These packages are all incorporated in the memoir class to one degree or another...

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

\newcommand{\Answer}[1]{\noindent{\color{purple!80!black}{{\sffamily Response:} }{#1}}}
\newcommand{\Comment}[1]{\item{\color{black}{{\sffamily Comment:} }{#1}}}

\usepackage{todonotes}
\newcommand{\TODO}[2][All]{{\todo[color=blue!20,inline]{{TODO (#1)}: #2}}}

%%% END Article customizations

%%% The "real" document content comes below...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors here                   %%
%%                                          %%
%% Specify information, if available,       %%
%% in the form:                             %%
%%   <key>={<id1>,<id2>}                    %%
%%   <key>=                                 %%
%% Comment or delete the keys which are     %%
%% not used. Repeat \author command as much %%
%% as required.                             %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{macros.tex}

\title{Response to reviewers\\[.3em]\OurTool{}:  Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles}
\author{
Afaf Saaidi \and
Delphine Allouche \and
Mireille Regnier \and
Bruno Sargueil \and
Yann Ponty}

\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
\maketitle

\section{General comments}

Points géneraux :

On a probablement pas été super clairs, mais :
Pas de comparaison entre protocoles, plutôt un test, rendu possible par IPANEMAP de la complémentarité des protocoles
Pas optimisation du traitement des donnés de sondage, mais traitement uniforme
Approche multi probing nous parait susceptible d’être robuste à l’incorporation d’une réactivité moins informative.

\section{Detailed responses}

\subsection*{Reviewer \#1}

\begin{enumerate}
	\Comment{The authors do not provide any sense of how raw data sets correlate in their experiments. They only analyze the ensembles of structures predicted based on their data. Thus for example, in Figure 5 we notice that the method of detection (CE) seems to be a far greater differentiator in predictions than the probe used (e.g. not all 1M7 cluster). The authors should add a panel clustering the raw probing data to compare it with the IPANEMAP clustering. This will require some clever design of distance metrics and mapping 1M7 to DMS maybe complex, but they should do a heat map like Figure 6 but with the raw data minimally.}

	\Answer{	On a fait ça, c’est en supp mat. On observe :
		Corrélation inverse entre distance à la native et MCC\%;
		Difficulté à regarder le clustering car peu significatif
	}

	\Comment{I am also concerned by the fact that they only have one (-) No Prob condition. For both CE and MaP data, a background subtraction is required. It is not at all clear what the No Prob condition is and why it was not independently subtracted from all the data prior to analysis.}

	\Answer{There is a misunderstanding here, the “(-) No Prob” conditions refers to a modeling process that does not use probing data as constraints. We understand that this was confusing and we no refer to it as “(-) No Exp” for modeling without experimental data. “(-) No Cons” for modeling without experimental constraints. Of course we have carried out control experiments without any modification reageant for each of the experiments reported, as now explicitly specified in the material and methods section.}

	\Comment{I am concerned the MaP data they collected is not reporting on structure. For example, quality controls need to be established showing that DMS reactivities follow expected profiles, i.e. A and C having higher mean reactivity that G and U.}

	\Answer{We understand this legitimate concern, expressed by multiple referees. The probing data reported on the structure for each probing conditions and reagents is now provided as supplementary material.
	Please note that the DMS results were not obtained following a ShapeMap-like strategy but by a “classical” RT-stop technique and Capilary electrophoresis.}

	\Comment{The main reason I am concerned with their MaP data is that they used superscript III instead of II for the RT. In the Smola paper, superscript III was attempted, but it was shown it does not detect adduct formation by mutation. If the CE to MaP correlations are low for the data, which I suspect they are, the authors will have to repeat MaP profiling with Superscript II to show this change in the protocol does not affect the data. I suspect however it will and may change the conclusions of the paper.}

	\Answer{It is exact that the Weeks laboratory uses an RNAse H minus mutant of the MMLV RT sold as “Superscript II” and advises to use it. However as far as we can tell from reviewing Dr Weeks bibliography, they never reported the test of “superscript III” (another RNAse H- mutant of the MMLV RT sold by the same company), and therefore never shown that does not detect the adduct. Actually in Smola et al. they specify “Reaction conditions have been optimized for SuperScript II reverse transcriptase only. Other reverse transcriptase enzymes and derivatives have not been tested and should not be used”. We tried superscript III in the conditions described and analysed the histograms provided by ShapeMapper which are metrics for the success of a shapeMap experiment as defined by smola et al. 2015.
	Please find below some examples of the histograms obtained using Superscript III:

	\begin{itemize}
	\item NMIA
	\TODO{Add plot}
	\item NMIA mg
	\TODO{Add plot}	
	\item 1M7
	\TODO{Add plot}
	\end{itemize}

	As can be seen on the right  histograms the read depth is sufficient (>10k reads/nucleotides) for these experiments to be interpreted. The histograms on the left shows that there are significantly more mutations in the modified (denatured and SHAPE) samples than in the untreated ones. These histograms are very similar to those shown by smola et al. as exemplary of a successful experiment. 
	In addition the shapeMap results are consistent with the X-ray structure (see figure XX in the supp. material), and their use with any prediction software as shown to improve the accuracy of the obtained model(s).

	In conclusion there is no doubt about the relevance of these results and we do not see the necessity to repeat them using superscript II.}

	\Comment{One possibility if the authors indeed find the MaP data is not correct because of superscript III would be to not include it in the analysis. Unfortunately this may somewhat temper the general interest of the paper, as a majority of SHAPE and probing data is now collected with MaP and -stop protocols.}

	\Answer{As described above, we did not find any reason to doubt the quality of those results, and believe they should remain included in our analysis.}

	\Comment{The authors also need to make their raw data available, I would recommend using the SNRNASM standard (PMID 21610212) and adding the files in the supplement. In addition the raw read files and alignments should really be deposited into the sequence read archive (SRA) so others can assess the quality of the mutation rates.}

	\Answer{We agree that raw data should be made available to the reader for the sake of reproducibility. Unfortunately, the SNANASM were no longer available at the time of this revision. We have informed the creators of the resource. In the meanwhile, we have thus deposited the reactivity results on the GitHub page of IPANEMAP, where they also serve as illustrative examples.

	The raw data were deposited to the SRA under identifier \TODO[Bruno]{Deposit data in SRA}.}

	\end{enumerate}

	\subsection*{Reviewer \#2}

	\begin{enumerate}
\Comment{I find this tool and study very interesting, especially the systematic assessment of the impact and combined power of various probing protocols for DiLCrz. To be ready for publication, the manuscript needs some further discussion of the DiLCrz results and a revision of the method presentation as detailed below.}

	\Answer{\TODO{...}}

	\Comment{The authors picked with DiLCrz a hard example since most problems of prediction accuracy are caused by the confusion of the nested structure model in the presence of the reactivities of the pseudoknot. That is, the quite stable PK-subhelix of length 4 (ignored in the nested model and the evaluation) will have a strong impact on reactivities that can not (correctly) be captured. Thus, the authors mainly evaluate how much the prediction of local structures in subsequence 65-120 is correct or not (as also visible in the reported structures within the supplement). Eventually, this also impacts the generality of the results.

	Thus, I think the authors should add a respective discussion to the manuscript.}

	\Answer{\TODO[Yann]{Check if we get better results by blocking the pseudoknot.}}

	\Comment{The methods section needs some reordering to first formaly introduce clusters and respective measures (stability/support) (e.g. in line 3-1-57) before introducing and discussing MBkM.

	For this restructuring, you might want to introduce the cummulative sample multi-set "$\mathcal{S} = \sum_d \mathcal{S}_d$" from which the clusters (also multi-sets?!) form a partitioning.}

	\Answer{\TODO{...}}

	\Comment{You do not introduce how you are able to compute MEA centroids without explicitely computing base pair probabilities. Checking your source code, I found the bp-probs are computed analogously to the structure probabilities, which is fine but should be explicitely mentioned to be reproducable.}

	\Answer{\TODO{...}}

	\Comment{It is totally unclear to me (and I didnt took the time to track it down in your code), how you derive an MEA for a cluster with structures from different reactivity data sets, since the same structure can be part of the cluster multiple times (with different probe-constraint probabilites). Do you sum up probe-specific probabilities in that case? Do you derive new base-pair probabilities for the cluster (and if so how)?
	Please provide somewhere details of your methods concerning the whole bp-prob and MEA centroid computation (at least in the supplementary material). Otherwise, your method description leaves out a central point of your algorithmic pipeline and renders is non-reproducable!}

	\Answer{\TODO{...}}

	\Comment{Please replace "kT" by "\text{R}T" in the structure probability formula (and whereever needed)!}

	\Answer{\TODO{...}}

	\Comment{What is the difference betwee the "cummulative probability of [a cluster's] structures" (line 3-1-58) and the formally introduced "Stability(C)" notion? If there is none, please use accordingly, otherwise provide respective details.}

	\Answer{\TODO{...}}

	\Comment{Please provide (eg in the supplement) some further details how to derived the values for m abd b for the Deigan method. So far, the description is quite vague.. }

	\Answer{\TODO{...}}

	\Comment{Within this context, you might want to discuss that too low pseudo-energy boni will yield similar results as hard constraints (which you want to avoid).}

	\Answer{\TODO{...}}

	\Comment{The formula for "$Stability(C)$" misses a "$\sum_{S\in C \cap \mathcal{S}_d}$" between the sum over d and the probability.}

	\Answer{\TODO{...}}

	\Comment{Please put brackets around the probability sum within the "$Support(C)$" definition to make clear that you are comparing $\tau$ to the sum.}

	\Answer{\TODO{...}}

	\Comment{If I get it right, if you are facing two clusters, one dominant in stability and the other in support, you will report two centroids, right?
	So reactivities that are inducing very high stability might dominate your prediction? Please check this hypothesis and if true discuss within the manuscript!}

	\Answer{\TODO{...}}

	\Comment{If you are NOT reporting multiple structures (as indicated in your results) how do you deal with cases illustrated above?}

	\Answer{\TODO{...}}

	\Comment{On page 7 you write "Fig. 5 suggests the presence of 8 clusters", which I do not agree... for me the PCA depiction would yield 4 clusters, i.e. B, C, D and the merge of all others. Thus, please rephrase the sentence or provide some other reason why you came up with 8 clusters from the beginning..}
	\Answer{\TODO{...}}

	\Comment{Concerning data normalization (Cordero et al.): when resetting all non-reacting position to 0, dont you loose the "background noise" of the experiment? 
	Did you test other options like subtracting the minimum/average/maximum of all non-reacting positions from all reactivities (before setting non-reacting to zero)?}

	\Comment{I would be very interested to see the performance of multi-probe predictions via RNAfold (MFE+MEA) when merging their reactivity data.
	For instance: just average the reactivities (per position) and provide them as new pseudo-reactivity data to RNAfold.
	While this might extremely mess up predictions, it might also yield similar effects as IPANEMAP, i.e. importance of contradicting reactivities is reduced the more experiments are considered..}

	\Answer{\TODO{...}}

	\Comment{Given your tool's documentation, a couple of questions arise that should be answered within the README.

	\begin{itemize}\item How are the reported free energies evaluated since your predictions are based on (multiple) reactivity-biased predictions? (your code hints at RNAeval calls, but please be verbose in the documentation to enable a clear intepretation of the results and comparability with other tools' output)\end{itemize}}

	\Answer{\TODO{...}}

	\Comment{\begin{itemize}\item How are the reported Boltzmann probabilities computed? based on the overall sample set? the respective cluster? (in both cases: what energies are used?) or based on the true (unconstraint) partition function computed e.g. by RNAfold?\end{itemize}}

	\Answer{\TODO{...}}

	\Comment{Given Table 1 (CMCT) and the general unawareness of the Nussinov-like MEA-optimization of the importance of base pair stacking, you might be able to further improve your results when implementing an MEA variant that excludes lonely base pairs.}

	\Answer{\TODO{...}}

	\Comment{I highly recommend to integrate IPANEMAP into the package management system conda via the bioconda channel. This would:
		\begin{itemize}
	\item be easy since IPANEMAP is eventually a set of python scripts (only a simple build and dependency script needs to be integrated into bioconda's recipes github repo)
	\item  handle all dependencies for the user
	\item ensure a simple installation of the tool and all dependencies 
	\item increase visibility of the tool
			\end{itemize}}

	\Answer{\TODO{...}}

	\Comment{When reading your work, it reminds me of another application, ie. the computation of unpaired probabilities for RNA-RNA interaction prediction in the presence of multiple probing data. For instance, see 
	https://doi.org/10.1093/bioinformatics/bty1029
	where single-experiment-reactivities were integrated (via Vienna package routines). 
	Given your pipeline, you should be able to derive suitable probabilities either directly from Pareto-optimal cluster(s) or from the overall sample set.}

	\Answer{\TODO{...}}

	\Comment{Fix the following typos/unfortunate choices of words:\begin{itemize}
	\item general: et al $\to$ et al.
	\item 1-2-30 : please provide the abbreviation details for SHAPE
	\item 1-1-21 : remove comma after "experiments"
	\item 1-2-37 : "more dynamics"
	\item 1-2-49 : "qualitative"
	\item 1-2-53 : "of individual nucleotides"
	\item 2-1-23 : "These include " beside structure optimization " the joint folding.."
	\item 2-1-49 : signal $\to$ signals
	\item 2-2-38 : criterion "are" $\to$ "is"
	\item 2-2-39 : identified $\to$ represented
	\item 3-1-5 and 8 : better replace "$R_i$" with "$d_i$", since you are using R for reference later on
	\item 3-1-60 : maybe replace "\#Datasets" with "$|\mathcal{D}|$" ?!
	\item 3-2-17 : missing "are" in "that both"
	\item 3-2-32 : move "where $k$ is the number of clusters" to line 40, where it is needed.
	\item 4-1-8 : Within the formula "$Dist(d,d')$" you have to replace "$x$" with "$i$"
	\item 4-1-52 : "Non-canonical" $\to$ "Crossing" or "Pseudoknot-forming"
	\item 5-1-40 : "metrics" $\to$ "metric"
	\item 6-2-44 : "hajdin" $\to$ "Hajdin"
	\item 8-1-31 : "Figure 1" $\to$ "6"
	\item 10-1-56 : "Figure" $\to$ "Table"
		\end{itemize}}	
	\end{enumerate}

	\subsection*{Reviewer \#3}

	\begin{enumerate}
	\Comment{My primary concern is that the authors use a pseudo-free energy formulation (page 3) with parameters that are the same for all conditions and probing reagents.  I am very surprised that this works.  The Diegan et al. work fit the parameters empirically for SHAPE data.  Sean Eddy [Annu. Rev. Biophys. 2014. 43:433] more explicitly drew the connection between these parameters and the log odds ratio of a nucleotide being paired, following earlier work of Sukosd et al. [Nucleic Acids Research. 2013. 41: 2807].  The Das lab [Biochemistry. 2012. 51: 7037] also explicitly fit the log odds for DMS data using gamma distributions.  I would expect that each probing reagent and each probing condition would need different parameters.}

		\Answer{We also expect that additional conversion formulae, and a specific parameter calibration, for each condition, would be beneficial in order to obtain better predictive performances. In fact, it is one of our project to produce more extensive data for a subset of the conditions explored in this study, and to attempt to systematically learn reactivities-to-pseudo-energy conversion models.

### 2019-11-16 SuppMat.tex

\section*{Multiprobing benchmark (Cordero~\emph{et al}~\cite{Cordero2012} dataset)}
\subsection*{MCC values of individual predictions}

@@

\begin{table}[H]
\centering
\newcommand{\B}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\BR}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\D}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\newcommand{\DR}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}lHHHHHHHHHHHHHHHH@{}}
 	\toprule
 	                              & \multicolumn{8}{l}{ \OurTool{}}                                     & \multicolumn{4}{l}{\Software{RNAfold} -- MFE mode} & \multicolumn{4}{l}{\Software{RNAfold} -- MEA mode}  \\
 	\textbf{CMCT}                 & \D    & \B    & \D       & \D    & \D    & \B       & \B    & \BR   & \D       & \D    & \B    & \DR                     & \D    & \D    & \B       & \D                       \\
 	\textbf{NMIA}                 & \D    & \D    & \B       & \D    & \B    & \D       & \B    & \BR   & \D       & \D    & \D    & \BR                     & \D    & \D    & \D       & \B                       \\
 	\textbf{DMS}                  & \D    & \D    & \D       & \B    & \B    & \B       & \D    & \BR   & \D       & \B    & \D    & \DR                     & \D    & \B    & \D       & \D                       \\ \midrule
 	5SRNA,E.Coli                  & 0.25  & 0.238 & 0.247    & 0.244 & 0.247 & 0.247    & 0.254 & 0.241 & 0.241    & 0.686 & 0.254 & 0.686                   & 0.241 & 0.686 & 0.269    & 0.686                    \\
 	glycineriboswitch,F.nucleatum & 0.568 & 0.627 & 0.868    & 0.952 & 0.868 & 0.658    & 0.868 & 0.868 & 0.306    & 0.313 & 0.395 & 0.313                   & 0.593 & 0.593 & 0.693    & 0.6                      \\
 	cidGMPriboswitch,V.Cholerae   & 0.654 & 0.77  & 0.654    & 0.77  & 0.654 & 0.77     & 0.654 & 0.77  & 0.77     & 0.77  & 0.667 & 0.77                    & 0.77  & 0.72  & 0.667    & 0.77                     \\
 	P4P6domain                    & 0.864 & 0.856 & 0.881    & 0.864 & 0.864 & 0.856    & 0.864 & 0.856 & 0.837    & 0.808 & 0.773 & 0.714                   & 0.845 & 0.808 & 0.781    & 0.722                    \\
 	adenineriboswitch,add         & 1     & 0.956 & 1        & 0.977 & 1     & 0.956    & 1     & 1     & 1        & 0.333 & 0.41  & 1                       & 1     & 0.333 & 0.356    & 0.306                    \\
 	tRNAphenylalanineyeast        & 0.286 & 0.746 & 0.976    & 0.746 & 0.976 & 0.746    & 0.976 & 0.976 & 0.976    & 0.976 & 0.976 & 0.976                   & 0.334 & 0.976 & 0.976    & 0.976                    \\ \midrule
 	Average                       & 0.604 & 0.7   & 0.77     & 0.76  & 0.77  & 0.705    & 0.77  & 0.785 & 0.69     & 0.65  & 0.58  & 0.74                    & 0.63  & 0.69  & 0.62     & 0.68                     \\ \bottomrule
 \end{tabular}
\end{adjustbox}
\caption{GM of the structures predicted with \OurTool{}, compared to predictions of \Software{RNAfold} in energy mimization (MFE) and accuracy maximization (MEA) modes.}
%( ref. $supplementary\_data/benchmark\_6RNAs$)}
\end{table}
\subsection*{Stablity analysis}
\begin{table}[H]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}\toprule
 &\multicolumn{3}{l}{ NMIA} & \multicolumn{3}{l}{ DMS} & \multicolumn{3}{l}{CMCT} &\multicolumn{3}{l}{ NMIA+DMS} & \multicolumn{3}{l}{ NMIA+CMCT} & \multicolumn{3}{l}{DMS+CMCT}& \multicolumn{3}{l}{NMIA+DMS+CMCT} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\

@@

%\section{IPANEMAP Vs Rsample}
\section*{Mono probing benchmark (Hajdin~\emph{et al}~\cite{Hajdin2013} dataset)}

@@

\subsection*{Detailed results of \OurTool{} and \Software{Rsample}}
\begin{table}[H]
	{\centering \begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
			\begin{tabular}{llllHllH}
				\toprule
				&        & \multicolumn{3}{l}{\Software{Rsample}}    & \multicolumn{3}{l}{\Software{IPANEMAP}}   \\
				{RNA} & Length & Sensitivity & PPV    & \multicolumn1c{GM} & Sensitivity & PPV    & \multicolumn1c{GM} \\ \midrule
				A     & 34     & 0.625       & 1      & 0.791              & 0.625       & 1      & 0.791              \\
				B     & 530    & 0.6622      & 0.6203 & 0.641              & 0.8986      & 0.8062 & 0.851              \\
				C     & 301    & 0.03        & 0.0313 & 0.031              & 0.6         & 0.6    & 0.6                \\
				D     & 214    & 0.6349      & 0.6667 & 0.651              & 0.7302      & 0.8519 & 0.789              \\
				E     & 500    & 0.6382      & 0.7823 & 0.707              & 0.5263      & 0.5517 & 0.539              \\
				F     & 47     & 0.4         & 0.75   & 0.548              & 0.6         & 0.75   & 0.671              \\
				G     & 118    & 0.7179      & 0.8    & 0.758              & 0.7692      & 0.8333 & 0.801              \\
				H     & 76     & 0.4762      & 0.5556 & 0.514              & 0.7619      & 0.7619 & 0.762              \\
				I     & 155    & 0.6786      & 0.8261 & 0.749              & 0.9821      & 0.9821 & 0.982              \\
				J     & 79     & 0.7727      & 0.85   & 0.81               & 0.9545      & 0.875  & 0.914              \\
				K     & 71     & 1           & 1      & 1                  & 1           & 0.9545 & 0.977              \\
				L     & 66     & 0.5625      & 0.6923 & 0.624              & 0.625       & 0.7143 & 0.668              \\
				M     & 79     & 0.6538      & 0.8095 & 0.727              & 0.6538      & 0.68   & 0.667              \\
				N     & 120    & 0.2857      & 0.2632 & 0.274              & 0.9714      & 0.9189 & 0.945              \\
				O     & 97     & 0.9286      & 0.9286 & 0.929              & 0.9286      & 0.8966 & 0.912              \\
				P     & 511    & 0.9328      & 0.7762 & 0.851              & 0.8908      & 0.7681 & 0.827              \\
				Q     & 401    & 0.5826      & 0.5583 & 0.57               & 0.7304      & 0.75   & 0.74               \\
				R     & 425    & 0.8397      & 0.8271 & 0.833              & 0.9084      & 0.8815 & 0.895              \\
				S     & 336    & 0.5481      & 0.6129 & 0.58               & 0.8077      & 0.866  & 0.836              \\
				T     & 473    & 0.7986      & 0.7143 & 0.755              & 0.8819      & 0.8194 & 0.85               \\
				U     & 412    & 0.5379      & 0.6174 & 0.576              & 0.75        & 0.8462 & 0.797              \\
				V     & 75     & 0.619       & 0.6842 & 0.651              & 0.619       & 0.5652 & 0.591              \\
				W     & 174    & 0.8095      & 0.8644 & 0.836              & 0.8095      & 0.9808 & 0.891              \\
				X     & 154    & 0.875       & 0.913  & 0.894              & 0.875       & 0.913  & 0.894              \\ \bottomrule
			\end{tabular}
		\end{adjustbox}\\}
\caption{\OurTool~ prediction performance compared to \Software{Rsample} tool}
\end{table}

\subsection*{Stability analysis}

@@

\section*{Case-study: Lariat capping ribozyme of {\itshape Didymium iridis}}
\subsection*{Compatibility of accessibility profiles with native and predicted structures}
We assess and validate the overall quality of probing data using a basic notion of distance between discretized profiles and structure. More precisely, given a secondary structure $S$ of length $n$, we define the {\bf 1D projection} of $S$ as the vector $v_S$ such that
$$ \forall i\in[1,n], v_S(i)=\begin{cases} 1 &\text{if $i$ unpaired in $S$}\\ 0 &\text{otherwise.} \end{cases} $$

>>>>

\tableofcontents

\section{Multiprobing benchmark (Cordero~\emph{et al}~\cite{Cordero2012} dataset)}
\subsection{MCC values of individual predictions}

@@

\begin{table}[H]
\centering
\newcommand{\B}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\BR}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\D}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\newcommand{\DR}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}lHHHHHHHHHHHHHHHH@{}}
 	\toprule
 	                              & \multicolumn{8}{l}{ \OurTool{}}                                     & \multicolumn{4}{l}{\Software{RNAfold} -- MFE mode} & \multicolumn{4}{l}{\Software{RNAfold} -- MEA mode}  \\
 	\textbf{CMCT}                 & \D    & \B    & \D       & \D    & \D    & \B       & \B    & \BR   & \D       & \D    & \B    & \DR                     & \D    & \D    & \B       & \D                       \\
 	\textbf{NMIA}                 & \D    & \D    & \B       & \D    & \B    & \D       & \B    & \BR   & \D       & \D    & \D    & \BR                     & \D    & \D    & \D       & \B                       \\
 	\textbf{DMS}                  & \D    & \D    & \D       & \B    & \B    & \B       & \D    & \BR   & \D       & \B    & \D    & \DR                     & \D    & \B    & \D       & \D                       \\ \midrule
 	5SRNA,E.Coli                  & 0.25  & 0.238 & 0.247    & 0.244 & 0.247 & 0.247    & 0.254 & 0.241 & 0.241    & 0.686 & 0.254 & 0.686                   & 0.241 & 0.686 & 0.269    & 0.686                    \\
 	glycineriboswitch,F.nucleatum & 0.568 & 0.627 & 0.868    & 0.952 & 0.868 & 0.658    & 0.868 & 0.868 & 0.306    & 0.313 & 0.395 & 0.313                   & 0.593 & 0.593 & 0.693    & 0.6                      \\
 	cidGMPriboswitch,V.Cholerae   & 0.654 & 0.77  & 0.654    & 0.77  & 0.654 & 0.77     & 0.654 & 0.77  & 0.77     & 0.77  & 0.667 & 0.77                    & 0.77  & 0.72  & 0.667    & 0.77                     \\
 	P4P6domain                    & 0.864 & 0.856 & 0.881    & 0.864 & 0.864 & 0.856    & 0.864 & 0.856 & 0.837    & 0.808 & 0.773 & 0.714                   & 0.845 & 0.808 & 0.781    & 0.722                    \\
 	adenineriboswitch,add         & 1     & 0.956 & 1        & 0.977 & 1     & 0.956    & 1     & 1     & 1        & 0.333 & 0.41  & 1                       & 1     & 0.333 & 0.356    & 0.306                    \\
 	tRNAphenylalanineyeast        & 0.286 & 0.746 & 0.976    & 0.746 & 0.976 & 0.746    & 0.976 & 0.976 & 0.976    & 0.976 & 0.976 & 0.976                   & 0.334 & 0.976 & 0.976    & 0.976                    \\ \midrule
 	Average                       & 0.604 & 0.7   & 0.77     & 0.76  & 0.77  & 0.705    & 0.77  & 0.785 & 0.69     & 0.65  & 0.58  & 0.74                    & 0.63  & 0.69  & 0.62     & 0.68                     \\ \bottomrule
 \end{tabular}
\end{adjustbox}
\caption{GM of the structures predicted with \OurTool{}, compared to predictions of \Software{RNAfold} in energy mimization (MFE) and accuracy maximization (MEA) modes.}
%( ref. $supplementary\_data/benchmark\_6RNAs$)}
\end{table}
\subsection{Stablity analysis}
\begin{table}[H]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}\toprule
 &\multicolumn{3}{l}{ NMIA} & \multicolumn{3}{l}{ DMS} & \multicolumn{3}{l}{CMCT} &\multicolumn{3}{l}{ NMIA+DMS} & \multicolumn{3}{l}{ NMIA+CMCT} & \multicolumn{3}{l}{DMS+CMCT}& \multicolumn{3}{l}{NMIA+DMS+CMCT} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\

@@

%\section{IPANEMAP Vs Rsample}
\section{Mono probing benchmark (Hajdin~\emph{et al}~\cite{Hajdin2013} dataset)}

@@

\subsection{Detailed results of \OurTool{} and \Software{Rsample}}
\begin{table}[H]
	{\centering \begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
			\begin{tabular}{llllHllH}
				\toprule
				&        & \multicolumn{3}{l}{\Software{Rsample}}    & \multicolumn{3}{l}{\Software{IPANEMAP}}   \\
				{RNA} & Length & Sensitivity & PPV    & \multicolumn1c{GM} & Sensitivity & PPV    & \multicolumn1c{GM} \\ \midrule
				A     & 34     & 0.625       & 1      & 0.791              & 0.625       & 1      & 0.791              \\
				B     & 530    & 0.6622      & 0.6203 & 0.641              & 0.8986      & 0.8062 & 0.851              \\
				C     & 301    & 0.03        & 0.0313 & 0.031              & 0.6         & 0.6    & 0.6                \\
				D     & 214    & 0.6349      & 0.6667 & 0.651              & 0.7302      & 0.8519 & 0.789              \\
				E     & 500    & 0.6382      & 0.7823 & 0.707              & 0.5263      & 0.5517 & 0.539              \\
				F     & 47     & 0.4         & 0.75   & 0.548              & 0.6         & 0.75   & 0.671              \\
				G     & 118    & 0.7179      & 0.8    & 0.758              & 0.7692      & 0.8333 & 0.801              \\
				H     & 76     & 0.4762      & 0.5556 & 0.514              & 0.7619      & 0.7619 & 0.762              \\
				I     & 155    & 0.6786      & 0.8261 & 0.749              & 0.9821      & 0.9821 & 0.982              \\
				J     & 79     & 0.7727      & 0.85   & 0.81               & 0.9545      & 0.875  & 0.914              \\
				K     & 71     & 1           & 1      & 1                  & 1           & 0.9545 & 0.977              \\
				L     & 66     & 0.5625      & 0.6923 & 0.624              & 0.625       & 0.7143 & 0.668              \\
				M     & 79     & 0.6538      & 0.8095 & 0.727              & 0.6538      & 0.68   & 0.667              \\
				N     & 120    & 0.2857      & 0.2632 & 0.274              & 0.9714      & 0.9189 & 0.945              \\
				O     & 97     & 0.9286      & 0.9286 & 0.929              & 0.9286      & 0.8966 & 0.912              \\
				P     & 511    & 0.9328      & 0.7762 & 0.851              & 0.8908      & 0.7681 & 0.827              \\
				Q     & 401    & 0.5826      & 0.5583 & 0.57               & 0.7304      & 0.75   & 0.74               \\
				R     & 425    & 0.8397      & 0.8271 & 0.833              & 0.9084      & 0.8815 & 0.895              \\
				S     & 336    & 0.5481      & 0.6129 & 0.58               & 0.8077      & 0.866  & 0.836              \\
				T     & 473    & 0.7986      & 0.7143 & 0.755              & 0.8819      & 0.8194 & 0.85               \\
				U     & 412    & 0.5379      & 0.6174 & 0.576              & 0.75        & 0.8462 & 0.797              \\
				V     & 75     & 0.619       & 0.6842 & 0.651              & 0.619       & 0.5652 & 0.591              \\
				W     & 174    & 0.8095      & 0.8644 & 0.836              & 0.8095      & 0.9808 & 0.891              \\
				X     & 154    & 0.875       & 0.913  & 0.894              & 0.875       & 0.913  & 0.894              \\ \bottomrule
			\end{tabular}
		\end{adjustbox}\\}
\caption{\OurTool~ prediction performance compared to \Software{Rsample} tool}
\end{table}

\subsection{Stability analysis}

@@

\section{Case-study: Lariat capping ribozyme of {\itshape Didymium iridis}}
\subsection{Correlation analysis of reactivities}
\subsection{Compatibility of accessibility profiles with native and predicted structures}
We assess and validate the overall quality of probing data using a basic notion of distance between discretized profiles and structure. More precisely, given a secondary structure $S$ of length $n$, we define the {\bf 1D projection} of $S$ as the vector $v_S$ such that
$$ \forall i\in[1,n], v_S(i)=\begin{cases} 1 &\text{if $i$ unpaired in $S$}\\ 0 &\text{otherwise.} \end{cases} $$
